Language Use in a Multilingual Tweet Corpus

### 2018-07-18 paper.tex

>>>>

Riga was chosen as the basis fro the geo-located collection, but the demographic in the city (larger proportion of ethinc Russians)  is different than in the rest of the country, especially its Western parts (larger proportion of ethnic Latvians). Taking this in the account, our global collection might be less biased that the geo-located one! However, it is an open question, whether geo-location of a larger area, for example, by tracking top 10 largest cities, improves the result.

Is it possible to control for bias using the tools described here? If we tracked more accounts that tweet dominantly in English, would that introduce other biases? Is it possible to select a mixture of topics such that every language would have few topics it dominates? How these topics should be explored?
